Evaluating infectious disease forecasts with allocation scoring rules

### 2023-09-08 alloscore_manuscript/alloscore-application.Rnw
Update alloscore_manuscript/alloscore-application.Rnw

In the supplement we show that in general, the components $x_i^{F,K}$ of the Bayes act are quantiles 
$F_i^{-1}(\tau)$ of the marginal forecasts $F_i$ for a probability level $\tau = \tau(K,F)$ that is defined by the constraint equation of the
allocation problem
\begin{align}
\sum_{i=1}^N F_i^{-1}(\tau) = K.
\end{align}
We note that $\tau(K,F)$ depends not only on the constraint level $K$ defining the decision problem but also on the forecast $F$. This is quite
different from the situation for quantile scores and the WIS, where the probability levels used to calculate scores are fixed.

>>>>

In the supplement we show that in general, the components $x_i^{F,K}$ of the Bayes act are quantiles 
$F_i^{-1}(\tau)$ of the marginal forecasts $F_i$ for a probability level $\tau = \tau(K,F)$ that solves the constraint equation of the
allocation problem
\begin{align}
\sum_{i=1}^N F_i^{-1}(\tau) = K.
\end{align}
We note that $\tau(K,F)$ depends not only on the constraint level $K$ defining the decision problem but also on the forecast $F$. This is quite
different from the situation for quantile scores and the WIS, where the probability levels used to calculate scores are fixed.
